Lensing

### 2015-02-17 Papers/ms.tex
Talking about simply parameterised and freeform models

\section{Introduction}
Galaxy-galaxy lensing is a powerful astrophysical tool for studying
the distribution of matter, including dark matter, in galaxies
\citep{treu}.

In recent years, several lens systems have been discovered which
are thought to contain at least one dark substructure
\citep{vegetti1, vegetti2, vegetti3}.

@@

All such choices involve tradeoffs between convenience and realism.
In a previous paper \citep{2011MNRAS.412.2521B} we argued that an ideal
modelling approach lies somewhere between simply-parameterised and
pixellated models. Simply parameterized models, such as Sérsic surface
brightness profiles for the source, and SIE models for the lens, are convenient,
they are clearly simplifications, and can produce misleading results if the
simple profiles are not a good approximation to the actual situation. On the
other hand, pixellated models for the source \citep[e.g.][]{suyu} or the lens
\citep[e.g.][]{2014MNRAS.445.2181C} can in principle represent ``any''
source surface brightness profile or lens density profile. However, the prior
distribution over pixel values is often chosen for mathematical convenience
\citep{2003ApJ...590..673W} and can assign virtually zero prior probability
to the hypothesis that the source actually looks like a galaxy.

>>>>

\section{Introduction}
Galaxy-galaxy lensing is a powerful astrophysical tool for studying
the distribution of matter, including dark matter, in galaxies
\citep{treu}. In recent years, several lens systems have been discovered which
are thought to contain at least one dark substructure
\citep{vegetti1, vegetti2, vegetti3}.

@@

All such choices involve tradeoffs between convenience and realism.
In a previous paper \citep{2011MNRAS.412.2521B} we argued that an ideal
modelling approach lies somewhere between simply-parameterised and
pixellated models. Simply parameterized models, such as Sérsic surface
brightness profiles for the source, and SIE models for the lens, are very
convenient. They only have a few adjustable parameters, and they capture
(to ``first order'') relevant prior information that we have about the
source and lens profiles. Of course, they are clearly simplifications,
and can produce misleading results if the actual profile is very different
from any member of the assumed family.

On the
other hand, pixellated models for the source \citep[e.g.][]{suyu} or the lens
\citep[e.g.][]{2014MNRAS.445.2181C} can in principle represent ``any''
source surface brightness profile or lens density profile. However, the prior
distribution over pixel values is often chosen to be a multivariate gaussian
for mathematical reasons, so
that the source can be analytically marginalized over
\citep{2003ApJ...590..673W}. Unfortunately, a multivariate gaussian prior
over pixel intensities can correspond to a very poor model of our prior
beliefs about the source. It assigns virtually zero prior probability
to the hypothesis that the source actually looks like a galaxy, and very high
prior probability to the hypothesis that the source looks like noise (or
blurred noise).
